---
title: "Assignment 2-Group project"
author: "Hai Huynh, Nguyen Do, Han Nguyen, Lam Huynh"
date: "2026-05-14"
output: html_document
---

LOAD

```{r}
library(tidyverse)
library(glmnet)
library(ggplot2)
library(dplyr)
library(pROC)
library(corrplot)
library(scales)
df <- read.csv("nsduh_assignment2_core.csv", stringsAsFactors = FALSE)
```

FILTER only required years and age categories

```{r}
df <- df %>%
  filter(year %in% c(2021, 2022, 2023),
         age_cat %in% c(1, 4))
```

DATA CLEANING

Response Variable

```{r}
df <- df %>% filter(!is.na(mde_past_year))
df$mde_past_year <- factor(df$mde_past_year, levels = c(0, 1), labels = c("No", "Yes"))
```

```{r}
# 94 = DON'T KNOW, 97 = REFUSED → recode as NA    
df$self_rated_health[df$self_rated_health %in% c(94, 97)] <- NA
df$self_rated_health <- factor(df$self_rated_health, levels = 1:5,
                                labels = c("Excellent","Very Good","Good","Fair","Poor"))
 
# --- employment ---
# 99 = 12-14 year olds (valid age group in age_cat=1); keep as its own level
df$employment <- factor(df$employment, levels = c(1, 2, 3, 4, 99),
                        labels = c("Full time","Part time","Unemployed","Other","Age 12-14"))
 
# --- income ---
df$income <- factor(df$income, levels = 1:4,
                    labels = c("<$20k","$20k-$49k","$50k-$74k","$75k+"))
 
# --- alcohol_consumption ---
df$alcohol_consumption <- factor(df$alcohol_consumption, levels = 1:6,
                                 labels = c("1-11 days","12-49 days","50-99 days",
                                            "100-299 days","300-365 days","Non-user"))
 
# --- risk_lsd_try ---
# 85 = BAD DATA, 94 = DON'T KNOW, 97 = REFUSED, 98 = BLANK → NA
df$risk_lsd_try[df$risk_lsd_try %in% c(85, 94, 97, 98)] <- NA
df$risk_lsd_try <- factor(df$risk_lsd_try, levels = 1:4,
                           labels = c("No risk","Slight risk","Moderate risk","Great risk"))
 
# --- ease_get_lsd ---
# 85/94/97/98 → NA
df$ease_get_lsd[df$ease_get_lsd %in% c(85, 94, 97, 98)] <- NA
df$ease_get_lsd <- factor(df$ease_get_lsd, levels = 1:5,
                           labels = c("Impossible","Very difficult","Fairly difficult","Fairly easy","Very easy"))
 
# --- hallucinogen_age_first ---
# 991 = never used (valid, keep as-is); 994/997/998 = unknown → NA
# 994/997/998 = unknown → NA
df$hallucinogen_age_first[df$hallucinogen_age_first %in% c(994, 997, 998)] <- NA

# 991 = never used → meaningful label, keeping real ages as-is
df$hallucinogen_age_first <- ifelse(df$hallucinogen_age_first == 991, "Never used", as.character(df$hallucinogen_age_first)
)
df$hallucinogen_age_first <- factor(df$hallucinogen_age_first)
# Note: 991 is intentionally kept — it means "never used hallucinogens"
 
# --- drove_on_hallucinogens ---
# 1=Yes, 2=No; 85/94/97/98 → NA (none present in filtered data but defensive coding)
df$drove_on_hallucinogens[df$drove_on_hallucinogens %in% c(85, 94, 97, 98)] <- NA
df$drove_on_hallucinogens <- factor(df$drove_on_hallucinogens,
                                     levels = c(1, 2), labels = c("Yes", "No"))
 
# --- Binary/factor conversions ---
df$sex_f                  <- factor(df$sex_f)
df$hallucinogen_past_year <- factor(df$hallucinogen_past_year, levels = c(0,1), labels = c("No","Yes"))
df$lsd_ever               <- factor(df$lsd_ever, levels = c(0,1), labels = c("No","Yes"))
df$lsd_past_year          <- factor(df$lsd_past_year, levels = c(0,1), labels = c("No","Yes"))
df$psilocybin_ever        <- factor(df$psilocybin_ever, levels = c(0,1), labels = c("No","Yes"))
df$alcohol_lastmonth      <- factor(df$alcohol_lastmonth, levels = c(0,1), labels = c("No","Yes"))
df$age_cat                <- factor(df$age_cat, levels = c(1, 4), labels = c("12-17","35+"))
df$hallucinogen_days_year <- factor(df$hallucinogen_days_year, levels = 1:6,labels = c("1-11 days","12-49 days","50-99 days","100-299 days","300-365 days","Non-user"))
df$year <- factor(df$year)
 
cat("Rows after removing missing response:", nrow(df), "\n")
cat("MDE prevalence:\n")
print(prop.table(table(df$mde_past_year)))
```

1.  Missing Data

```{r}
cat("\n--- Missing Data Summary ---\n")
missing_summary <- df %>%
  summarise(across(everything(), ~ sum(is.na(.)))) %>%
  pivot_longer(everything(), names_to = "Variable", values_to = "Missing_Count") %>%
  mutate(Missing_Pct = round(Missing_Count / nrow(df) * 100, 1)) %>%
  filter(Missing_Count > 0) %>%
  arrange(desc(Missing_Count))
 
print(missing_summary)
 
# Plot: Missing data
ggplot(missing_summary, aes(x = reorder(Variable, Missing_Pct), y = Missing_Pct)) +
  geom_col(fill = "steelblue") +
  coord_flip() +
  labs(title = "Missing Data by Variable",
       x = NULL, y = "% Missing") +
  theme_minimal()
```

2.  RESPONSE VARIABLE: CLASS BALANCE

```{r}
cat("\n--- MDE Class Balance ---\n")
mde_table <- df %>%
  count(mde_past_year) %>%
  mutate(pct = round(n / sum(n) * 100, 1))
print(mde_table)
 
# Plot: Class balance
ggplot(mde_table, aes(x = mde_past_year, y = n, fill = mde_past_year)) +
  geom_col(width = 0.5, show.legend = FALSE) +
  geom_text(aes(label = paste0(pct, "%")), vjust = -0.5, size = 4) +
  scale_fill_manual(values = c("steelblue", "tomato")) +
  labs(title = "Class Distribution of Major Depressive Episode (MDE)",
       subtitle = "Note the class imbalance — MDE cases are the minority",
       x = "MDE Past Year", y = "Count") +
  theme_minimal()
 
```

--\> use AUC and F1 over accuracy

MDE Rate

```{r}
mde_rate <- function(data, var) {
  data %>%
    filter(!is.na(.data[[var]])) %>%
    group_by(across(all_of(var))) %>%
    summarise(n    = n(),
              rate = mean(mde_past_year == "Yes"),
              se   = sqrt(rate * (1 - rate) / n),
              .groups = "drop") %>%
    mutate(lower = pmax(0, rate - 1.96 * se),
           upper = pmin(1, rate + 1.96 * se),
           label = paste0(round(rate * 100, 1), "%"))
}
```

3.  MDE Rate by Age Group

```{r}

mde_rate(df, "age_cat") %>%
  ggplot(aes(x = age_cat, y = rate, fill = age_cat)) +
  geom_col(width = 0.5, show.legend = FALSE) +
  geom_text(aes(label = label), vjust = -0.8, size = 4) +
  scale_fill_manual(values = c("steelblue","tomato")) +
  scale_y_continuous(labels = percent_format(),
                     expand = expansion(mult = c(0, 0.15))) +
  labs(title = "Plot 3: MDE Rate by Age Group",
       x = "Age Group", y = "MDE Rate") +
  theme_minimal()
```

4.  MDE Rate by Sex

```{r}
mde_rate(df, "sex_f") %>%
  ggplot(aes(x = sex_f, y = rate, fill = sex_f)) +
  geom_col(width = 0.5, show.legend = FALSE) +
  geom_text(aes(label = label), vjust = -0.8, size = 4) +
  scale_fill_manual(values = c("steelblue","tomato")) +
  scale_y_continuous(labels = percent_format(),
                     expand = expansion(mult = c(0, 0.15))) +
  labs(title = "Plot 4: MDE Rate by Sex",
       x = "Sex", y = "MDE Rate") +
  theme_minimal()
```

5.  MDE Rate by Age Group and Sex (interaction)

```{r}
df %>%
  group_by(age_cat, sex_f) %>%
  summarise(rate = mean(mde_past_year == "Yes"), .groups = "drop") %>%
  ggplot(aes(x = age_cat, y = rate, fill = sex_f)) +
  geom_col(position = "dodge", width = 0.6) +
  geom_text(aes(label = paste0(round(rate * 100, 1), "%")),
            position = position_dodge(0.6), vjust = -0.5, size = 3.5) +
  scale_y_continuous(labels = percent_format(),
                     expand = expansion(mult = c(0, 0.15))) +
  scale_fill_manual(values = c("steelblue","tomato")) +
  labs(title = "Plot 5: MDE Rate by Age Group and Sex",
       x = "Age Group", y = "MDE Rate", fill = "Sex") +
  theme_minimal()
```

PLOT 6 — MDE Rate by Self-Rated Health

```{r}
mde_rate(df, "self_rated_health") %>%
  ggplot(aes(x = self_rated_health, y = rate, group = 1)) +
  geom_line(colour = "steelblue", linewidth = 1.2) +
  geom_point(colour = "steelblue", size = 3) +
  geom_text(aes(label = label), vjust = -1, size = 3.5) +
  scale_y_continuous(labels = percent_format(),
                     expand = expansion(mult = c(0.05, 0.2))) +
  labs(title = "Plot 6: MDE Rate by Self-Rated Health",
       x = "Self-Rated Health", y = "MDE Rate") +
  theme_minimal()
```

PLOT 7 — MDE Rate by Hallucinogen Use Past Year

```{r}
mde_rate(df, "hallucinogen_past_year") %>%
  ggplot(aes(x = hallucinogen_past_year, y = rate, fill = hallucinogen_past_year)) +
  geom_col(width = 0.5, show.legend = FALSE) +
  geom_text(aes(label = label), vjust = -0.8, size = 4) +
  scale_fill_manual(values = c("steelblue","tomato")) +
  scale_y_continuous(labels = percent_format(),
                     expand = expansion(mult = c(0, 0.15))) +
  labs(title = "Plot 7: MDE Rate by Hallucinogen Use (Past Year)",
       x = "Used Hallucinogens Past Year", y = "MDE Rate") +
  theme_minimal()
```

PLOT 8 — MDE Rate by Income

```{r}
mde_rate(df, "income") %>%
  ggplot(aes(x = income, y = rate, fill = income)) +
  geom_col(width = 0.6, show.legend = FALSE) +
  geom_text(aes(label = label), vjust = -0.8, size = 3.5) +
  scale_fill_brewer(palette = "Blues", direction = -1) +
  scale_y_continuous(labels = percent_format(),
                     expand = expansion(mult = c(0, 0.15))) +
  labs(title = "Plot 8: MDE Rate by Income Level",
       x = "Income", y = "MDE Rate") +
  theme_minimal()
```

PLOT 9 — MDE Rate by Perceived Risk of Trying LSD

```{r}
mde_rate(df, "risk_lsd_try") %>%
  ggplot(aes(x = risk_lsd_try, y = rate, group = 1)) +
  geom_line(colour = "tomato", linewidth = 1.2) +
  geom_point(colour = "tomato", size = 3) +
  geom_text(aes(label = label), vjust = -1, size = 3.5) +
  scale_y_continuous(labels = percent_format(),
                     expand = expansion(mult = c(0.05, 0.2))) +
  labs(title = "Plot 9: MDE Rate by Perceived Risk of Trying LSD",
       x = "Perceived Risk", y = "MDE Rate") +
  theme_minimal()
 
```

PLOT 10 — MDE Rate by Employment

```{r}
mde_rate(df, "employment") %>%
  ggplot(aes(x = employment, y = rate, fill = employment)) +
  geom_col(width = 0.6, show.legend = FALSE) +
  geom_text(aes(label = label), vjust = -0.8, size = 3.5) +
  scale_fill_brewer(palette = "Set2") +
  scale_y_continuous(labels = percent_format(),
                     expand = expansion(mult = c(0, 0.15))) +
  labs(title = "Plot 10: MDE Rate by Employment Status",
       x = "Employment Status", y = "MDE Rate") +
  theme_minimal()
```

PLOT 11 — MDE Rate Over Time

```{r}
mde_rate(df, "year") %>%
  ggplot(aes(x = year, y = rate, group = 1)) +
  geom_line(colour = "steelblue", linewidth = 1.2) +
  geom_point(colour = "steelblue", size = 3) +
  geom_text(aes(label = label), vjust = -1, size = 3.5) +
  scale_y_continuous(labels = percent_format(),
                     expand = expansion(mult = c(0.05, 0.2))) +
  labs(title = "Plot 11: MDE Rate Over Time (2021-2023)",
       x = "Year", y = "MDE Rate") +
  theme_minimal()
 
```

# MODELS

### Ridge Regression

```{r}
library(glmnet)
library(caret)
library(pROC)

set.seed(123)



# 1. TRAIN / TEST SPLIT (80/20)


train_idx <- sample(nrow(df), size = 0.8 * nrow(df))
train_df  <- df[train_idx, ]
test_df   <- df[-train_idx, ]

cat("Train size:", nrow(train_df), "\n")
cat("Test size: ", nrow(test_df),  "\n")


# =============================================================================
# 2. IMPUTE REMAINING NAs
# glmnet cannot handle NAs — fill with median (numeric) or mode (factor)
# =============================================================================

impute <- function(x) {
  if (is.factor(x)) {
    mode_val <- names(sort(table(x), decreasing = TRUE))[1]
    x[is.na(x)] <- mode_val
  } else {
    x[is.na(x)] <- median(x, na.rm = TRUE)
  }
  x
}

train_imp <- train_df %>% mutate(across(everything(), impute))
test_imp  <- test_df  %>% mutate(across(everything(), impute))


# =============================================================================
# 3. MODEL MATRIX
# Converts factors to dummy variables — required by glmnet
# Done separately on train and test to avoid data leakage
# =============================================================================

X_train <- model.matrix(mde_past_year ~ . - 1, data = train_imp)
X_test  <- model.matrix(mde_past_year ~ . - 1, data = test_imp)

y_train <- train_imp$mde_past_year
y_test  <- test_imp$mde_past_year


# =============================================================================
# 4. CROSS-VALIDATION TO SELECT LAMBDA
# alpha = 0 → Ridge (L2 penalty)
# 10-fold CV optimising for AUC
# =============================================================================

cv_ridge <- cv.glmnet(
  x            = X_train,
  y            = y_train,
  family       = "binomial",
  alpha        = 0,
  nfolds       = 10,
  type.measure = "auc"
)

lambda_best <- cv_ridge$lambda.min   # lambda with best CV AUC
lambda_1se  <- cv_ridge$lambda.1se   # slightly more regularised, often preferred

cat("\nBest lambda (min):  ", round(lambda_best, 6), "\n")
cat("Lambda 1SE:          ", round(lambda_1se,  6), "\n")

# Plot 1: CV curve — AUC vs log(lambda)
plot(cv_ridge, main = "Ridge CV: AUC vs log(Lambda)")


# =============================================================================
# 5. FIT FINAL MODEL using lambda.1se
# =============================================================================

ridge_model <- glmnet(
  x      = X_train,
  y      = y_train,
  family = "binomial",
  alpha  = 0,
  lambda = lambda_1se
)

# Plot 2: Coefficient shrinkage paths
plot(glmnet(X_train, y_train, family = "binomial", alpha = 0),
     xvar = "lambda", label = FALSE,
     main = "Ridge: Coefficient Paths vs log(Lambda)")
abline(v = log(lambda_1se), lty = 2, col = "red")
legend("topright", legend = "Selected lambda (1SE)", lty = 2, col = "red")


# =============================================================================
# 6. PREDICTIONS
# =============================================================================

prob_train <- predict(ridge_model, newx = X_train, type = "response")[, 1]
prob_test  <- predict(ridge_model, newx = X_test,  type = "response")[, 1]

pred_train <- factor(ifelse(prob_train >= 0.5, "Yes", "No"), levels = c("No","Yes"))
pred_test  <- factor(ifelse(prob_test  >= 0.5, "Yes", "No"), levels = c("No","Yes"))


# =============================================================================
# 7. PERFORMANCE METRICS
# =============================================================================

cat("\n=== IN-SAMPLE (Train) ===\n")
cm_train <- confusionMatrix(pred_train, y_train, positive = "Yes")
print(cm_train)

cat("\n=== OUT-OF-SAMPLE (Test) ===\n")
cm_test <- confusionMatrix(pred_test, y_test, positive = "Yes")
print(cm_test)

# AUC
roc_train <- roc(y_train, prob_train, levels = c("No","Yes"), direction = "<", quiet = TRUE)
roc_test  <- roc(y_test,  prob_test,  levels = c("No","Yes"), direction = "<", quiet = TRUE)

cat("\nTrain AUC:", round(auc(roc_train), 4), "\n")
cat("Test  AUC:", round(auc(roc_test),  4), "\n")

# Plot 3: ROC curve
plot(roc_test,  col = "steelblue", lwd = 2,
     main = paste("Ridge ROC Curve — Test AUC:", round(auc(roc_test), 4)))
plot(roc_train, col = "tomato", lwd = 2, lty = 2, add = TRUE)
legend("bottomright", legend = c("Test","Train"),
       col = c("steelblue","tomato"), lty = c(1,2), lwd = 2)


# =============================================================================
# 8. SUMMARY TABLE
# =============================================================================

results_ridge <- data.frame(
  Metric    = c("Accuracy", "Sensitivity", "Specificity", "Precision", "F1", "AUC"),
  Train     = c(
    round(cm_train$overall["Accuracy"],       4),
    round(cm_train$byClass["Sensitivity"],    4),
    round(cm_train$byClass["Specificity"],    4),
    round(cm_train$byClass["Pos Pred Value"], 4),
    round(cm_train$byClass["F1"],             4),
    round(auc(roc_train),                     4)
  ),
  Test      = c(
    round(cm_test$overall["Accuracy"],        4),
    round(cm_test$byClass["Sensitivity"],     4),
    round(cm_test$byClass["Specificity"],     4),
    round(cm_test$byClass["Pos Pred Value"],  4),
    round(cm_test$byClass["F1"],              4),
    round(auc(roc_test),                      4)
  )
)

cat("\n=== RIDGE PERFORMANCE SUMMARY ===\n")
print(results_ridge)

# Save results for model comparison later
cm_train -> cm_train_ridge
cm_test  -> cm_test_ridge
roc_train -> roc_train_ridge
roc_test  -> roc_test_ridge

```

```{r}


library(rpart)
library(rpart.plot)
library(caret)
library(pROC)


# =============================================================================
# 1. FIT INITIAL TREE (cp = 0 grows full unpruned tree)
# set.seed placed here because xerror in cp table uses random sampling
# — without this, xerror changes every run (see tutorial note)
# =============================================================================

set.seed(123)
tree_model <- rpart(
  mde_past_year ~ .,
  data    = train_df,
  method  = "class",
  cp      = 0
)


# =============================================================================
# 2. FIND BEST CP USING CROSS-VALIDATION ERROR (xerror)
# =============================================================================

# Print cp table
printcp(tree_model)

# Plot CV error vs tree size
plotcp(tree_model, main = "Classification Tree: CV Error vs Tree Size")

# Pick cp with lowest xerror
best_cp <- tree_model$cptable[which.min(tree_model$cptable[, "xerror"]), "CP"]
cat("\nBest cp:", round(best_cp, 6), "\n")


# =============================================================================
# 3. PRUNE TREE TO BEST CP
# =============================================================================

tree_pruned <- prune(tree_model, cp = best_cp)


# =============================================================================
# 4. PLOT THE PRUNED TREE
# =============================================================================

rpart.plot(tree_pruned,
           type  = 4,
           extra = 104,
           main  = "Pruned Classification Tree: MDE Prediction")


# =============================================================================
# 5. PREDICTIONS
# =============================================================================

# Class labels for confusion matrix
pred_train <- predict(tree_pruned, newdata = train_df, type = "class")
pred_test  <- predict(tree_pruned, newdata = test_df,  type = "class")

# Probabilities for AUC
prob_train <- predict(tree_pruned, newdata = train_df, type = "prob")[, "Yes"]
prob_test  <- predict(tree_pruned, newdata = test_df,  type = "prob")[, "Yes"]


# =============================================================================
# 6. PERFORMANCE METRICS
# =============================================================================

cat("\n=== IN-SAMPLE (Train) ===\n")
cm_train <- confusionMatrix(pred_train, train_df$mde_past_year, positive = "Yes")
print(cm_train)

cat("\n=== OUT-OF-SAMPLE (Test) ===\n")
cm_test <- confusionMatrix(pred_test, test_df$mde_past_year, positive = "Yes")
print(cm_test)

# AUC
roc_train <- roc(train_df$mde_past_year, prob_train,
                 levels = c("No","Yes"), direction = "<", quiet = TRUE)
roc_test  <- roc(test_df$mde_past_year,  prob_test,
                 levels = c("No","Yes"), direction = "<", quiet = TRUE)

cat("\nTrain AUC:", round(auc(roc_train), 4), "\n")
cat("Test  AUC:", round(auc(roc_test),  4), "\n")

# ROC Curve
plot(roc_test,  col = "steelblue", lwd = 2,
     main = paste("Classification Tree ROC — Test AUC:", round(auc(roc_test), 4)))
plot(roc_train, col = "tomato", lwd = 2, lty = 2, add = TRUE)
legend("bottomright", legend = c("Test", "Train"),
       col = c("steelblue", "tomato"), lty = c(1, 2), lwd = 2)


# =============================================================================
# 7. SUMMARY TABLE
# =============================================================================

results_tree <- data.frame(
  Metric = c("Accuracy", "Sensitivity", "Specificity", "AUC"),
  Train  = c(
    round(cm_train$overall["Accuracy"],    4),
    round(cm_train$byClass["Sensitivity"], 4),
    round(cm_train$byClass["Specificity"], 4),
    round(auc(roc_train),                  4)
  ),
  Test   = c(
    round(cm_test$overall["Accuracy"],     4),
    round(cm_test$byClass["Sensitivity"],  4),
    round(cm_test$byClass["Specificity"],  4),
    round(auc(roc_test),                   4)
  )
)

cat("\n=== CLASSIFICATION TREE PERFORMANCE SUMMARY ===\n")
print(results_tree)

# Save for model comparison later
cm_train -> cm_train_tree
cm_test  -> cm_test_tree
roc_train -> roc_train_tree
roc_test  -> roc_test_tree

```

Random Forest

```{r}
library(ranger)
library(caret)
library(pROC)
library(vip)
 
 
# =============================================================================
# 1. FIT RANDOM FOREST
# =============================================================================
 
p <- ncol(train_df) - 1   # number of predictors
 
set.seed(123)
rf_model <- ranger(
  formula     = mde_past_year ~ .,
  data        = train_df,
  mtry        = floor(p / 3),
  importance  = "impurity",
  probability = TRUE
)
 
rf_model
 
 
# =============================================================================
# 2. VARIABLE IMPORTANCE PLOT
# =============================================================================
 
vip(rf_model)
 
 
# =============================================================================
# 3. PREDICTIONS
# =============================================================================
 
rf_pred_test  <- predict(rf_model, test_df)
rf_pred_train <- predict(rf_model, train_df)
 
prob_test  <- rf_pred_test$predictions[,  "Yes"]
prob_train <- rf_pred_train$predictions[, "Yes"]
 
# Class labels
rf_class_test  <- factor(ifelse(prob_test  > 0.5, "Yes", "No"), levels = c("No", "Yes"))
rf_class_train <- factor(ifelse(prob_train > 0.5, "Yes", "No"), levels = c("No", "Yes"))
 
 
# =============================================================================
# 4. CONFUSION MATRIX
# =============================================================================
 
cat("\n=== IN-SAMPLE (Train) ===\n")
# Replace lines 669-672 with:
cm_train <- confusionMatrix(rf_class_train, train_df$mde_past_year, positive = "Yes")
print(cm_train)

cm_test <- confusionMatrix(rf_class_test, test_df$mde_past_year, positive = "Yes")
print(cm_test)
 
 
# =============================================================================
# 5. ROC AND AUC
# =============================================================================
 
roc_train <- roc(train_df$mde_past_year, prob_train,
                 levels = c("No", "Yes"), direction = "<", quiet = TRUE)
roc_test  <- roc(test_df$mde_past_year,  prob_test,
                 levels = c("No", "Yes"), direction = "<", quiet = TRUE)
 
cat("\nTrain AUC:", round(auc(roc_train), 4), "\n")
cat("Test  AUC:", round(auc(roc_test),  4), "\n")
 
plot(roc_test,  col = "steelblue", lwd = 2,
     main = paste("Random Forest ROC — Test AUC:", round(auc(roc_test), 4)))
plot(roc_train, col = "tomato", lwd = 2, lty = 2, add = TRUE)
legend("bottomright", legend = c("Test", "Train"),
       col = c("steelblue", "tomato"), lty = c(1, 2), lwd = 2)




cm_train -> cm_train_rf
cm_test  -> cm_test_rf
roc_train -> roc_train_rf
roc_test  -> roc_test_rf
```

Comparison

```{r}
comparison <- data.frame(
  Metric        = c("Train Accuracy", "Test Accuracy", "Train AUC", "Test AUC"),
  Ridge         = c(
    round(cm_train_ridge$overall["Accuracy"], 8),
    round(cm_test_ridge$overall["Accuracy"],  8),
    round(auc(roc_train_ridge),               8),
    round(auc(roc_test_ridge),                8)
  ),
  Classification_Tree          = c(
    round(cm_train_tree$overall["Accuracy"],  8),
    round(cm_test_tree$overall["Accuracy"],   8),
    round(auc(roc_train_tree),                8),
    round(auc(roc_test_tree),                 8)
  ),
  Random_Forest = c(
    round(cm_train_rf$overall["Accuracy"],    8),
    round(cm_test_rf$overall["Accuracy"],     8),
    round(auc(roc_train_rf),                  8),
    round(auc(roc_test_rf),                   8)
  )
)
 
print(comparison)
```



